---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# xkcd

<!-- badges: start -->
<!-- badges: end -->

The `xkcd` package provides an R interface to retrieve data about [xkcd comics](https://xkcd.com) from the xkcd website - and most importantly, view these comics in the plot window! 

## Installation

You can install the development version of xkcd from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ssusnea/xkcd")
```

## Browsing Comics

Given a comic number the `xkcd` function retrieves a JSON object with metadata about that comic.

```{r example}
library(xkcd)

first_comic <- xkcd(1)
first_comic
```

The most useful thing you can do with these objects is plot them, which displays the comic image in the plot window. 

```{r}
plot(first_comic)
```

